\documentclass[12pt]{article}
\input{packages-and-defs}

\begin{document}


% - atm it stresses more teamplay and makes me look like a team player
% - I need to emphasize more of my personal qualities
% - plans for the postdoc 
% - 


\subsection*{Adam Goli{\'n}ski - request for a recommendation letter}

The hard deadline for the application including the reference letters is at noon on Wednesday 3rd March 2021 (closest Wednesday).

% \vspace{10pt}
\textbf{Brief personal statement}\\
During my time as a postdoc I intend to primarily contribute to the area of data compression.
I believe my understanding of the field and probabilistic modelling skillset, 
together with the expertise of other group members and leaders in deep learning architectures, equivariance, and meta-learning,
are a great combination to make good progress in this area.

Apart from the topic of compression, 
I also intend to finish my few open projects and  
assist other projects that would benefit from my knowledge of amortized and simulation-based inference.

Personally,
I am confident I have built the level of technical proficiency that allows me to come up with research ideas and execute them. 
I know when, and to whom, to turn for advice when I need it.
I believe I possess the interpersonal skills required to successfully collaborate with peers, assemble adequate project teams, and provide day-to-day mentorship and guidance to junior students, 
as exemplified by several of my successful collaborations.


\vspace{10pt}
\textbf{Details about the reference letter}\\
The job description doesn't say how long the they expect the reference letter to be, they only say " a short statement in support of your application".

In your letter, I would like to ask you to comment on those of the following that you can provide positive recommendation about:
\begin{itemize}
\item My personal capacity and skillset,
\item The fit of my proposed research topic to the interests and expertise available in the group,
\item The value of my existing collaborations in the department (with Tom, Tim, Anthony, Emilien) that would continue if I could stay as a postdoc,
\item My involvement in the organisation and documentation of the computational resources in the research group, and day-to-day help I provide to group members on that front.
\item The level of interaction you would be able to offer for me as per as per the job description: 
"Statements should directly indicate the level of interaction that the person expects to offer during the position, should the application be successful."
\end{itemize}

Could you please email your reference letter directly to the Recruitment Coordinator at vacancies@maths.ox.ac.uk, quoting vacancy reference 149619?

The other person I have asked for a reference letter is Tom.



\vspace{10pt}
\textbf{Full list of projects}
\begin{itemize}
\item \textbf{Faithful Inversion of Generative Models for Effective Amortized Inference}. \\
Stefan Webb, \underline{Adam Goli{\'n}ski}, Robert Zinkov, N. Siddharth, Tom Rainforth, Yee Whye Teh, Frank Wood. \\
NeurIPS 2018. 
\item \textbf{Amortised Monte Carlo Integration}. \\
\underline{Adam Goli{\'n}ski}$^{*}$, Frank Wood, Tom Rainforth$^{*}$. \\
ICML 2019, Best Paper Honourable Mention award.
\item \textbf{Improving Normalising Flows via Better Orthogonal Parameterizations}. \\
\underline{Adam Goli{\'n}ski}$^{*}$, Mario Lezcano-Casado$^{*}$, Tom Rainforth. \\
ICML 2019 Workshop on Invertible Neural Networks and Normalizing Flows (INNF).
\item \textbf{Target–Aware Bayesian Inference}.\\
Tom Rainforth$^{*}$, \underline{Adam Goli{\'n}ski}$^{*}$, Frank Wood, Sheheryar Zaidi. \\
JMLR, 2020.
\item \textbf{Feedback Recurrent Autoencoder for Video Compression}.\\
\underline{Adam Goli{\'n}ski}$^{*}$, Reza Pourreza$^{*}$, Yang Yang$^{*}$, Guillaume Sautiére, Taco S Cohen. \\
ACCV 2020.
\item \textbf{Expectation Programming}.\\
Tim Reichelt, \underline{Adam Goli{\'n}ski}, Luke Ong, Tom Rainforth.\\
Submitted to ICML 2021.
\item \textbf{Effective Approximate Inference for Nested Simulators}. \\
Bradley Gram-Hansen$^{*}$, \underline{Adam Goli{\'n}ski}$^{*}$, [...], Yee Whye Teh, Atılım Güneş Baydin, Tom Rainforth.\\
Rejected from AISTATS 2021, planning to add more experiments and submit to NeurIPS 2021 or AISTATS 2022. \\
\item \textbf{Lossless Compression using Continuously Indexed Normalising Flows}.\\
Anthony Caterini$^{*}$, \underline{Adam Goli{\'n}ski}$^{*}$.\\
Submitting to ICLR 2021 Neural Compression Workshop.
\item \textbf{Neural Function Representation Compression}.\\
Emilien Dupont$^{*}$, \underline{Adam Goli{\'n}ski}$^{*}$, Milad Alizadeh, Arnaud Doucet, Yee Whye Teh.\\
Submitting to ICLR 2021 Neural Compression Workshop.
\item \textbf{Improving Inference for Thermodynamic Variational Objective}. \\
Rob Brekelmans$^{*}$, \underline{Adam Goli{\'n}ski}$^{*}$, Vaden Masrani, Roger Grosse, Alireza Makhzani. \\
Planning to submit to NeurIPS 2021.
\end{itemize}


\vspace{10pt}
\textbf{The project I am most proud of: AMCI and TABI}\\
The project I am most proud of so far is Amortised Monte Carlo Integration and Target–Aware Bayesian Inference.
It was the first project I was driving since the inception and I have been responsible for in every aspect.
Out of all the projects I have worked on so far, 
I feel that this one is going to age best as
% , rather than making an incremental contribution in the zeitgeist of current research, 
we point people's attention to a fundamental limitation of a very popular inference algorithm 
(which was known but not particularly appreciated by wider audience) 
and introduce a range of methods that sidestep that limitation.
Our work is likely to become a standard reference about this issue. 
The idea was appreciated by the ACs and we were awarded Best Paper Honourable Mention at ICML 2019.
% During the course of this project I have established good working understanding of many Monte Carlo methods, 
% ways to pursue debugging of probabilistic models and inference methods, 
% and implemented a personal toolbox of those methods that are now serving me well in other projects.
What is more, this project now provides motivation for follow up work such as \emph{Expectation Programming},
and an opportunity for me to contribute as a mentor for junior students.
 % rather than first author.



\end{document}
